\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2019-01-08 archive.tex
deep program learning paragraph in introduction

We call our system `DreamCoder' because it acquires these two kinds of
expertise through a novel kind of wake/sleep or `dream'
learning~\cite{hinton1995wake}, iterating through a wake cycle --
where it solves problems by writing programs -- and a pair of sleep
cycles, both of which are loosely biologically inspired by actual
human sleep.  The first sleep cycle, which we refer to as
\textbf{consolidation}, grows the DSL by replying experiences from
waking and consolidating them into new code abstractions.  This cycle
is inspired by the formation of abstractions during sleep memory
consolidation~\cite{DUDAI201520}.  The second sleep cycle, which we
refer to as \textbf{dreaming}, improves the agents knowledge of how to
write programs by training a neural network to help search for
programs. The neural net is trained on replayed experiences as well as
`fantasies', or samples, from the DSL.  These two kinds of dreams are
inspired by the distinct episodic replay and hallucination components
of dream sleep~\cite{fosse2003dreaming}.

This dream-learning architecture brings together two lines of prior work,
both of which have been separately influential within
artificial intelligence.
One line of work
considers the problem of learning new concepts, abstractions, or
`options' from
experience~\cite{Dechter:2013:BLV:2540128.2540316,DBLP:conf/icml/LiangJK10,solomonoff1989system,DBLP:journals/corr/abs-1110-5667,stolle2002learning},
while the other line of work considers the problem of learning how to
deploy those concepts
efficiently~\cite{devlin2017robustfill,balog2016deepcoder,NGDS}.  Our
goal with DreamCoder is to show that the combination of these ideas is
uniquely powerful, and pushes us toward program-writing systems that,
like human learners, autonomously acquire the expertise needed to
navigate a new domain of problems.

@@

\noindent\textbf{\system Hyperparameters}
Due to the high computational cost we
performed only an informal coarse
hyperparameter search.
The most important parameter is
the enumeration timeout during the wake phase;
domains that present more challenging program synthesis
problems require either longer timeouts, more CPUs, or both.
\begin{center}
  \begin{tabular}{ccccccc}
    \toprule
    Domain&Timeout&CPUs&Batch size&$\lambda$ (Sec.~\ref{consolidationSection})&$\alpha$ (\ref{mapAppendix})&Max frontier (\ref{systemPseudocode})\\\midrule
    Lists&7m&64&10&1&30&5\\
    Text&7m&64&10&1&30&5\\
    Graphics&1h&128&40&1&30&5\\
    Symbolic regression& & 40&10 & 1&30&5\\
    Towers& & 64&10 & 1&30&5\\
    Regexes& & 64&10 & 1&30&5\\
    \bottomrule

  \end{tabular}
\end{center}

>>>>

We call our system `DreamCoder' because it acquires these two kinds of
expertise through a novel kind of wake/sleep or `dream'
learning~\cite{hinton1995wake}, iterating through a wake cycle --
where it solves problems by writing programs -- and a pair of sleep
cycles, both of which are loosely biologically inspired by actual
sleep.  The first sleep cycle, which we refer to as
\textbf{consolidation}, grows the DSL by replying experiences from
waking and consolidating them into new code abstractions.  This cycle
is inspired by the formation of abstractions during sleep memory
consolidation~\cite{DUDAI201520}.  The second sleep cycle, which we
refer to as \textbf{dreaming}, improves the agents knowledge of how to
write programs by training a neural network to help search for
programs. The neural net is trained on replayed experiences as well as
`fantasies', or samples, from the DSL.  These two kinds of dreams are
inspired by the distinct episodic replay and hallucination components
of dream sleep~\cite{fosse2003dreaming}.

\begin{comment}
This dream-learning architecture brings together two lines of prior work,
both of which have been separately influential within
artificial intelligence.
One line of work
considers the problem of learning new concepts, abstractions, or
`options' from
experience~\cite{Dechter:2013:BLV:2540128.2540316,DBLP:conf/icml/LiangJK10,solomonoff1989system,DBLP:journals/corr/abs-1110-5667,stolle2002learning},
while the other line of work considers the problem of learning how to
deploy those concepts
efficiently~\cite{devlin2017robustfill,balog2016deepcoder,NGDS}.  Our
goal with DreamCoder is to show that the combination of these ideas is
uniquely powerful, and pushes us toward program-writing systems that,
like human learners, autonomously acquire the expertise needed to
navigate a new domain of problems.
\end{comment}

Each wake/sleep cycle creates new DSL components that build on
components learned in earlier sleep cycles, growing a DSL with nested 
hierarchies of code.  We identify this cumulative nesting of
abstractions as a kind of deep representation
learning~\cite{lecun2015deep}.  Figure~\ref{exampleDSL} diagrams a
subset of these learned networks (the DSL). For example, the system
learns to sort sequences of numbers by invoking a DSL component 4
layers deep, or draws the leftmost pairs of images in
Figure~\ref{exampleDSL} using a depth-3 component.  For this reason we
refer to \system as an instance of `deep program learning'.

@@

\noindent\textbf{\system Hyperparameters}
Due to the high computational cost we
performed only an informal coarse
hyperparameter search.
The most important parameter is
the enumeration timeout during the wake phase;
domains that present more challenging program synthesis
problems require either longer timeouts, more CPUs, or both.
\begin{center}
  \begin{tabular}{ccccccc}
    \toprule
    Domain&Timeout&CPUs&Batch size&$\lambda$ (Sec.~\ref{consolidationSection})&$\alpha$ (\ref{mapAppendix})&Max frontier (\ref{systemPseudocode})\\\midrule
    Lists&7m&64&10&1&30&5\\
    Text&7m&64&10&1&30&5\\
    Graphics&1h&128&40&1&30&5\\
    Symbolic regression& & 40&10 & 1&30&5\\
    Towers& & 64&10 & 1&30&5\\
    Regexes& & 64&10 & 1&30&5\\
    \bottomrule     
  \end{tabular}
\end{center}
